Foreign Exchange Speculation: An Event Study

### 2018-01-16 MDPI/MDPI_template/FinStudies.tex
Updated some parts of the introduction

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage[flushleft]{threeparttable}
\usepackage{changes}
%\usepackage[comma, sort&compress]{natbib}% Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

@@

\begin{document}
\section{Introduction}
If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} for example emphasise the role that speculation plays in facilitating financial market transactions. Speculators offer a service for a fee that is determined by the return on their activity.  While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.   However, the later \citet[p. 101]{Keynes1936} regarded speculation as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd' and \citet{Delong1990noise} provides a model of cases where speculative noise provides a constrain on informed traders benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added[remark=1]{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

The debate about the relative merit of these two concepts of speculation continues to the current era where there has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  A common story that has encouraged congressional investigation says that wild speculation drove oil and other commodities prices well above their fundamental value causing harship for commodity consumers and a subsequent collapse that was equally disruptive for the producders.  See \citet{} and \citet{} for fuller details.  However, \citet{} argues that this is not the case and this is backed by \citet{}}

This paper evaluates the relative importance of these two concepts of speculation by investigating the relationship between the intensity of speculation and the weight of speculative positions relative to subsequent movement of foreign exchange prices.\footnote{\label{FX}The foreign exchange market is chosen for this study because it is the largest and most liquid financial market in the world.  The latest survey taken by the Bank for International Settlements (BIS) in April 2016 estimated average daily turnover at \$5.1trn with average daily spot transactions of \$1.7trn See \citet{BISFX2016}.  The cost of trading in this market, when measured in terms of the size of the bid-ask spread, is extremely low. An analysis by \citet{Steely2013} of the bid-ask spreads for USD-JPY, GBP-USD and EUR-USD for the period January 2001 to 2005 finds that the average spread for each is 0.342\%, 0.305\% and 0.326\% respectively.  This would be the cost for a round-trip (buying and selling immediately).}  \added[remark=2]{The intenisty of speculation is measured with the use of option risk-reversal skew.  As these become more extreme it signals that expectations of buyers and sellers in the foreign exchange options market have diverged significantly from the forward rate.  Weight of speculative positions is measured by the net long or short of speculative accounts in the futures market. If the movement of prices towards equilibrium, \emph{price discovery} is facilitated by order flow from informed traders (as has been asserted theoetically by \citet{Glosten1985Bid} and \citet{Kyle1985Continuous} while being demonstrted empirically by \citet{Lyons1995Microstructure} and \citet{Evans2002Order} and \citet{rime2010exchange}, speculative sentiment and positions would be part of the price discovery process if informed and would disript this process if not. Therefore,}if speculators are informed their activity drives exchange rates towards equilibrium and prices should follow a random walk after these extremes \added[remark=3]{of speculative sentiment or position}; if speculators are uninformed and their activity can be regarded as noise, the most extreme speculative sentiment and the time when speculators have the greatest weight in the market should correspond with the greatest deviation of prices from fundamental value, when reversals are most likely to take place.

@@

\section{Measuring speculation}
\replaced{This study uses a unique series of option}{A set of} \emph{risk-reversal skews}\added{are used} to measure \delete{of} speculative sentiment\footnote{\deleted{It appears that this is the only period for which the data currently exist.  The risk-reversal data is very difficult to obtain in an over-the-counter market like foreign exchange where there is no centralised exchange to record and collect information, generally being the property of quoting institutions.}  The risk-reversals are the average prices quoted at 10:00 GMT by major banks on the Thomson-Reuters composite option pages (OPT1)  for the period between January 2 1996 and September 6 2002.  The risk-reversals are the spread of implied volatility for a 1 month 25 delta at-the-money call option relative to the equivalent put.  Risk-reversal skew is the relative price of currency put and call options for the same strike price.}\delete{, as well as CFTC data on speculative positions.} The risk-reversal skew is the relationship between a call option and the equivalent put.    If the exchange rate is expected to follow a random walk with drift towards the 1 month forward \added[remark=4]{the same maturity as the option}, implied volatility on the put and the call for the same delta should be equal.  Any deviation from this equivalence is an indication that a divergence from the random walk with drift is implied in the market price of options.

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage[flushleft]{threeparttable}
\usepackage{changes}
\setremarkmarkup{(#2)}
%\usepackage[comma, sort&compress]{natbib}% Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

@@

\begin{document}
\section{Introduction}
\added{Speculation can be stabilising or destabilising.} If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} \deleted{for example} emphasise the role that speculation plays in facilitating financial market transactions \added{by providing liquidity that allows hedgers and other market participants to swiftly find counterparties with the need for large prices concessions.}. Speculators offer a service for a fee that is determined by the return on their activity.  \replaced{While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.}{\citet{FriedmanPositive} argued that even where there are a mixture of infomed and unnformed speculators, the informed woudl tend to buy when prices were below intrinsic value and sell when above, making profits, stabilising the market and driving the loss-making uninformed speculators out of teh market.} \deleted{However, the later} \citet[p. 101]{Keynes1936} \added{also had a later, more negative view of speculation.  Here he} regarded speculation as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd'\added{. Uninformed speculators may dominate} and \citet{Delong1990noise} provides a model of cases where speculative noise provides a constraint on informed traders benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

The debate about the relative merit of these two concepts of speculation continues to the current era where there has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  A common story that has encouraged congressional investigation says that wild speculation drove oil and other commodities prices well above their fundamental value causing harship for commodity consumers and a subsequent collapse that was equally disruptive for the producders.  \citet{PindyckSpec} show a broad movement of commodities prices not linked to fundaments that they argue is caused by speculation.  \citet{TangSpec} suggest that this speculative disruption was exacerbated by speculation on commodity indices.  However, \citet{ScottSpec} do not find a link between speculative positions and excess price movements in commodities.   \citet{Jacksspec} documents the history of attacks on speculation following price volatility.}

This paper evaluates the relative importance of these two concepts of speculation by investigating the relationship between the intensity of speculation and the weight of speculative positions relative to subsequent movement of foreign exchange prices.\footnote{\label{FX}The foreign exchange market is chosen for this study because it is the largest and most liquid financial market in the world.  The latest survey taken by the Bank for International Settlements (BIS) in April 2016 estimated average daily turnover at \$5.1trn with average daily spot transactions of \$1.7trn See \citet{BISFX2016}.  The cost of trading in this market, when measured in terms of the size of the bid-ask spread, is extremely low. An analysis by \citet{Steely2013} of the bid-ask spreads for USD-JPY, GBP-USD and EUR-USD for the period January 2001 to 2005 finds that the average spread for each is 0.342\%, 0.305\% and 0.326\% respectively.  This would be the cost for a round-trip (buying and selling immediately).}  \added{The intenisty of speculation is measured with the use of option risk-reversal skew.  As these become more extreme it signals that expectations of buyers and sellers in the foreign exchange options market have diverged significantly from the forward rate.  Weight of speculative positions is measured by the net long or short of speculative accounts in the futures market. If the movement of prices towards equilibrium, \emph{price discovery} is facilitated by order flow from informed traders (as has been asserted theoetically by \citet{Glosten1985Bid} and \citet{Kyle1985Continuous} while being demonstrted empirically by \citet{Lyons1995Microstructure} and \citet{Evans2002Order} and \citet{rime2010exchange}, speculative sentiment and positions would be part of the price discovery process if informed and would disript this process if not. Therefore,}if speculators are informed their activity drives exchange rates towards equilibrium and prices should follow a random walk after these extremes \added{of speculative sentiment or position}; if speculators are uninformed and their activity can be regarded as noise, the most extreme speculative sentiment and the time when speculators have the greatest weight in the market should correspond with the greatest deviation of prices from fundamental value, when reversals are most likely to take place.

@@

\section{Measuring speculation}
\replaced{This study uses a unique series of option}{A set of} \emph{risk-reversal skews}\added{are used} to measure \delete{of} speculative sentiment\footnote{\deleted{It appears that this is the only period for which the data currently exist.  The risk-reversal data is very difficult to obtain in an over-the-counter market like foreign exchange where there is no centralised exchange to record and collect information, generally being the property of quoting institutions.}  The risk-reversals are the average prices quoted at 10:00 GMT by major banks on the Thomson-Reuters composite option pages (OPT1)  for the period between January 2 1996 and September 6 2002.  The risk-reversals are the spread of implied volatility for a 1 month 25 delta at-the-money call option relative to the equivalent put.  Risk-reversal skew is the relative price of currency put and call options for the same strike price.}\delete{, as well as CFTC data on speculative positions.} The risk-reversal skew is the relationship between a call option and the equivalent put.    If the exchange rate is expected to follow a random walk with drift towards the 1 month forward \added{the same maturity as the option}, implied volatility on the put and the call for the same delta should be equal.  Any deviation from this equivalence is an indication that a divergence from the random walk with drift is implied in the market price of options.
